\chapter{Related Publications}
\section{Journals}

\begin{itemize}
\item
K. Alonso and M. Datcu, "Accelerated Probabilistic Learning Concept for Mining Heterogeneous Earth Observation Images," \textit{IEEE Journal of Selected Topics in Applied Earth Observations and Remote Sensing}, vol. 8, no. 7, pp. 3356-3371, July 2015.
\item
K. Alonso, D. Espinoza-Molina, and M. Datcu, “Multilayer Architecture for Heterogeneous Geospatial Data Analytics: Querying and Understanding EO Archives,” \textit{IEEE Journal of Selected
Topics in Applied Earth Observations and Remote Sensing}, vol. 10, no. 3, pp. 791-801, March 2017.

\item
K. Alonso, D. Espinoza-Molina, and M. Datcu, “Mining Multitemporal in-situ Heterogeneous Monitoring Information for the Assurance of Recorded Land Cover Changes,” \textit{IEEE Journal of Selected
Topics in Applied Earth Observations and Remote Sensing}, vol. 10, no. 3, pp. 877-887, March 2017.

\end{itemize}



\section{Conferences}
\begin{itemize}
\item
K. Alonso and M. Datcu, "Accelerated Knowledge-Driven Image Mining System for Data Fusion in Big Data," in \textit{Proc. ESA-EUSC-JRC 9th Conference on Image Information Mining. The Sentinels Era}, Bucharest, pp. 97-100, 2014. %doi:10.2788/25852

\item
K. Alonso and M. Datcu, "Image Information Mining: an Accelerated Bayesian Algorithm for Data Fusion of SAR Big Data," in\textit{ Proc. 10th European Conference on Synthetic Aperture Radar (EUSAR)}, Berlin, pp. 1-4, 2014.

\item
K. Alonso and M. Datcu, "Knowledge-driven image mining system for Big Earth Observation data fusion: GIS maps inclusion in active learning stage," in \textit{Proc. IEEE Geoscience and Remote Sensing Symposium (IGARSS)}, Quebec City, QC, pp. 3538-3541, 2014.
%doi: 10.1109/IGARSS.2014.6947246

\item
K. Alonso, D. Espinoza-Molina and M. Datcu, "LUCAS Visual Browser: A tool for land cover visual analytics," in \textit{Proc. IEEE International Geoscience and Remote Sensing Symposium (IGARSS)}, Milan, pp. 1484-1487, 2015.
%doi: 10.1109/IGARSS.2015.7326060

\item
D. Espinoza-Molina, K. Alonso, G. Schwarz and M. Datcu, "Big Data Analytics for Detailed Urban Mapping," in \textit{Proc. Mapping Urban Areas from Space (MUAS)}, Frascati, 2015. 

\item
D. Espinoza-Molina, K. Alonso and M. Datcu, "Visual Analytics for Semantic Queries of TerraSAR-X Image Content," in \textit{Proc. SPIE Remote Sensing Conference}, Toulouse, pp. 1-10, 2015.

\item
D. Espinoza-Molina, K. Alonso and M. Datcu, "Semantic Indexing of TerraSAR-X and in situ data for urban analytics," in \textit{Proc. International Archives of the Photogrammetry, Remote Sensing and Spatial Information Sciences (ISPRS)}, Kish Island, pp. 185-188, 2015.
%doi: 10.5194/isprsarchives-XL-1-W5-185-2015.

\item
D. Espinoza-Molina, K. Alonso and M. Datcu, "Visual Data Mining for Exploration of the Feature Space Using In-situ Data," in \textit{Proc. IEEE Geoscience and Remote Sensing Symposium (IGARSS)}, Beijing, pp. 3538-3541, 2016.
\end{itemize}
